---
title: "Pokemon"
author: "Fahada_Alsehami"
date: "2/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = T,tidy =  FALSE,highlight = TRUE)
options(digits=3)
```


```{r}
# Load the required packsges into memory:
library(readr)
library(pander)
library(tidyverse)
library(janitor)
library(dplyr, warn.conflicts = F)
library(gridExtra)
library(plyr)
library(reshape2)
library(rsconnect)
library(knitr)
library(ggplot2)
```




```{r}
# Setup Pokemon project to Shiny.io server
rsconnect::setAccountInfo(name='pokemon',
			  token='903D7CF589541470913C6979207B0113',
			  secret='yVUCDBa6Y4uErHCqgiRqRxgkhkAmdwa+eycbDpRp')
```

```{r}
# Deploy Pokemon project to Shiny.io server
library(rsconnect)
library(shiny)
deployApp()
```

```{r}
Pokemon <- read_csv("Pokemon.csv")
View(Pokemon)
```

```{r}
##Dataset including variables were recorded:
head(Pokemon)
```



```{r}
#Rename some variables to make our variable's name handy
Pokemon <- rename(Pokemon, c(`Type 1` = "Type1", `Type 2` = "Type2", `Sp. Atk` = "Spec.Atk", `Sp. Def` = "Spec.Def"))
Pokemon
```


#Express the Generation column as a factor
```{r}
#Vectorize function of the Generation as a factor
Pokemon$Generation <- as.factor(Pokemon$Generation)
Pokemon
```

```{r}
#Here will describe the structure of Pokemon dataset:
str(Pokemon)
```


#2 Pre-processing Pokemon Dataset

#2.1 
# levels provides access to the levels attribute of a variable. The first form returns the value of the levels of its argument and the second sets the attribute.


#2.1 (Pokemon Type 1)
```{r}
# We set a factor to Pokemon$Type1 to represnt the Pokemon  one type as catefory data:
type1_level <- factor(Pokemon$Type1)
# We used levels function to obtain the value of Pokemon wiht Type 1
levels(type1_level)
```
#2.2 (Pokemon Type 2)
```{r}
# We set a factor to Pokemon$Type2 to represnt the Pokemon  one type as catefory data:
type2_level <- factor(Pokemon$Type2)
# Also, we used levels function to obtain the value of Pokemon wiht Type 1
levels(type2_level)
```

```{r}
# Here will plot how many primary Pokemon of Type1 has by using Geom bar:
ggplot(Pokemon, aes(x=fct_infreq(Type1))) + 
  geom_bar(fill="#fff00f", colour="red") +
  labs(x="Type1", y="Frequency") +
  theme(axis.text.x=element_text(angle=45, hjust=1))
```
# We have about XXXXX



```{r}
# Here will plot how many primary Pokemon of Type2 has by using Geom bar:
ggplot(Pokemon, aes(x=fct_infreq(Type2))) + 
  geom_bar(fill="#ff0011", colour="blue") +
  labs(x="Type2", y="Frequency") +
  theme(axis.text.x=element_text(angle=45, hjust=1))
```
# As shown in the graph above describe the Pokemon with two types, and we notice that we have the hiehst freqi=uency is NA. However, we believe that NA is a XXX

```{r}
# Here we used the decisiion tree
treeMap <- Pokemon %>%
  mutate(Type2 = ifelse(is.na(Type2), paste("only", Type1), Type2),
         Type1 = Type1) %>%
  group_by(Type2, Type1) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  treemap::treemap(index = c("Type1", "Type2"),
                   vSize = "n", vColor = "Type1")

```
```{r}
#Here will define three types of Pokemons 
type.string <- c('Grass', 'Fire', 'Water')
type.colors <- c('#27A632', '#F07800', '#94D6CE')
type.subcolors <- c('#27938E','#D81800','#56A9ED')
theme_set(theme_minimal(base_size = 15))
```

```{r}
#Here will combine the Pokemon's types which will be represnted by "types"
library(dplyr) 

types <- Pokemon %>% 
     group_by(Type1, Type2) %>%
     summarise(count=n()) 
types
```
```{r}
ggplot(types, aes(x=Type1,y=Type2)) +
  geom_tile(aes(fill=count)) +
  geom_text(aes(label=count)) +
  theme(axis.text.x=element_text(angle=45, hjust=1)) +
  labs(x="Type1", y="Type2") +   
  scale_fill_gradient(low="white", high="blue") 
```

```{r}
# Histogram of HP
hp <- ggplot(Pokemon, aes(x=HP)) +
  geom_histogram(binwidth=4, fill="blue2", colour="black") + 
  labs(x="Hit Point", y="Freq") 

# Histogram of Attack
attk <- ggplot(Pokemon, aes(x=Attack)) +
  geom_histogram(binwidth=4, fill="indianred1", colour="black") + 
  labs(x="Pokemon Attack", y="Freq") 

# Histogram of Defense
defn <- ggplot(Pokemon, aes(x=Defense)) +
  geom_histogram(binwidth=4, fill="violet", colour="black") + 
  labs(x="Pokemon Defense", y="Freq") 

# Histogram of Special Attack
speedAtk <- ggplot(Pokemon, aes(x=Spec.Atk)) +
  geom_histogram(binwidth=4, fill="hotpink4", colour="black") + 
  labs(x="Special Attack", y="Freq") 

# Histogram of Special Defense
speedDef <- ggplot(Pokemon, aes(x=Spec.Def)) +
  geom_histogram(binwidth=4, fill="brown2", colour="black") + 
  labs(x="Special Defense", y="Freq") 

# Histogram of Speed
speedp <- ggplot(Pokemon, aes(x=Speed)) +
  geom_histogram(binwidth=4, fill="darkorchid2", colour="black") + 
  labs(x="Pokemon Speed", y="Freq") 

# Histogram of Total 
pokTotal <- ggplot(Pokemon, aes(x=Total)) +
  geom_histogram(binwidth=4, fill="lightgoldenrod1", colour="black") + 
  labs(x="Total", y="Freq") 

# Subplot with all the histograms 
grid.arrange(hp, attk, defn, speedAtk, speedDef, speedp, pokTotal,
             layout_matrix=cbind(c(1,4,7), c(2,5,7), c(3,6,7)))
```

```{r}
# We created a denisty plot for all variables we have to distingush the Legendray from the normal :

d1 <- ggplot(Pokemon, aes(x=HP, fill=Legendary)) +
  geom_density(alpha=.8) +
  labs(x="Hit Point", y="Density") +
  theme(legend.position="none")

d2 <- ggplot(Pokemon, aes(x=Attack, fill=Legendary)) +
  geom_density(alpha=0.8) +
  labs(x="Attack", y="Density") +
  theme(legend.position="none")

d3 <- ggplot(Pokemon, aes(x=Defense, fill=Legendary)) +
  geom_density(alpha=0.8) +
  labs(x="Defense", y="Density") +
  theme(legend.position="none")


d4 <- ggplot(Pokemon, aes(x=Spec.Atk, fill=Legendary)) +
  geom_density(alpha=0.8) +
  labs(x="Special Attack", y="Density") +
  theme(legend.position="none")


d5 <- ggplot(Pokemon, aes(x=Spec.Def, fill=Legendary)) +
  geom_density(alpha=0.8) +
  labs(x="Special Defense", y="Density") +
  theme(legend.position="none")

d6 <- ggplot(Pokemon, aes(x=Speed, fill=Legendary)) +
  geom_density(alpha=0.8) +
  labs(x="Speed", y ="Density") +
  theme(legend.position="none")

d7 <- ggplot(Pokemon, aes(x=Total, fill=Legendary)) +
  geom_density(alpha=0.8) +
  labs(x="Total", y="Density") 

grid.arrange(d1, d2, d3, d4, d5, d6, d7,
             layout_matrix=cbind(c(1,4,7), c(2,5,7), c(3,6,7)))
```
# As the denisty curves for all of the variables we have of Pokemons show that the Normal Pokemons have less statistics than the Legendry Pokemans.  

# Boxplot should be include here 









#Our Specific objectives:

1. What is the minimum number of characteristics needed to determine a Pokemon’s type?
2. What is the minimum number of characteristics needed to determine a Pokemon’s generation? 
3. If we were to create a new pokemon with the random characteristic assignment, what would its predicted type be based on kNN, PCA, and random forest techniques? 


#Cross-Validation method:
# i will supply the updated code for the CV ASAP:
```{r}
glm.fit = glm(data = Pokemon)
cv.glm(Pokemon, glm.fit)$delta
```
# We will constructed Random Forest Algorthim to ....
```{r}
# Prep :
set.seed(12121)
library(caret)
train.index <- createDataPartition(Pokemon$total, p = .80, list = FALSE)
train <- Pokemon[ train.index,]
test  <- Pokemon[-train.index,]
```
```{r}
## Smoted Data
set.seed(1234)
library(randomForest)
library(miscTools)
library(ggplot2)
class(Pokemon$total)
str(Pokemon)
rf = randomForest(total~.,Pokemon[,-c(1:2)],ntree=500,mtry=2,nodesize=1, rules = TRUE)
rf_test_predictions = predict(rf, test)

(r2 <- rSquared(test$total, test$total - predict(rf, test[,-5])))
(mse <- mean((test$total - predict(rf, test[,-5]))^2))
```
```{r}
######## Homoskedastic errors ##########
p <- ggplot(aes(x=actual, y=pred),
            data=data.frame(actual=test$total, pred=predict(rf, test[,-5])))
p + geom_point() +
  geom_abline(color="red") +
  ggtitle(paste("RandomForest Regression in R r^2=", r2, sep=""))
```
```{r}
## Variable Importance List
rf_var_imp = data.frame(rf$importance)
rf_var_imp$Variables = row.names(rf_var_imp)
rf_var_imp
```


#Hierarchical clustering
```{r}
library(dplyr)
d<-dist(Pokemon[,-c(2,3,4,13)],method="euclidean")
fit<-hclust(d,method = "average")
plot(fit,main="Pokemon Tree",col.main="blue",xlab="average pokemon",ylab="height")
pok.clust<-cutree(fit,h = 300)
table(pok.clust)
#pie(table(Pokemon$Type1),col=c("blue","red","green"))
```

# Decision Tree:
```{r}
Sample <- sample_n(Pokemon,200,replace = FALSE)
model_pl_1 <- randomForest(Pokemon[,-ncol(train_data)], train_data[,ncol(train_data)], test_data[,-ncol(test_data)], test_data[,ncol(test_data)], ntree=50)

```
```{r}
#Decision Tree
Sample <- sample_n(Pokemon,200,replace = FALSE)
LegendPok <- subset(Sample,Sample$Legendary=="True")
NoLegPok <- subset(Sample,Sample$Legendary=="False")
library(rpart)
Sample<-sample_n(Pokemon,200,replace = FALSE)
LegendPok<-subset(Sample,Sample$Legendary=="True")
NoLegPok<-subset(Sample,Sample$Legendary=="False")
modeltree<-rpart(Type1~.,data =NoLegPok[,-c(2,4,13)])
plot(modeltree,main="Desicion Tree",col.main="purple")
text(modeltree, use.n=TRUE,col="red")
prediction<-predict(modeltree,newdata=LegendPok,type="class")
table(prediction,LegendPok$Type1)
```
```{r}

data(Pokemon, package = "ggplot2")

set.seed(123)
data <- sample_n(Pokemon, 300)

modlss <- loess(HP ~ Attack, data = data)
fit <- arrange(augment(Attack), HP)

highchart() %>%
  hc_add_series(data, type = "scatter",
                hcaes(x = HP, y = Attack, size = depth, group = cut)) %>%
  hc_add_series(fit, type = "line", hcaes(x = HP, y = .fitted),
                name = "Fit", id = "fit") %>%
  hc_add_series(fit, type = "arearange",
                hcaes(x = HP, low = .fitted - 2*.se.fit,
                      high = .fitted + 2*.se.fit),
                linkedTo = "fit")
```


